---
docname: CV
name: Win
surname: Cowger
position: "Environmental Scientist"
address: "Moore Institute for Plastic Pollution Research"
profilepic: "./Professional_photo.jpg"
phone: +1 515 298 3869
www: wincowger.com
email: "wincowger@gmail.com"
twitter: Win_OpenData
github: wincowgerDEV
orcid: 0000-0001-9226-3104
linkedin: win-cowger-6273b0136
date: "`r format(Sys.time(), '%B %Y')`"
headcolor: "689d6a"
aboutme: "Win is working to use science, data, and software to tackle the global challenges of plastic pollution and waste."
output: vitae::awesomecv
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(vitae)
library(googlesheets4)
library(dplyr)
library(glue)
googlesheets4::gs4_deauth()
data <- read_sheet('https://docs.google.com/spreadsheets/d/1E3_Z900RAWbRnThNNu-_DXQqZN6qHkD2wN7ZYGmKt34/edit?usp=sharing') %>%
    mutate(ShortDescription = ifelse(!is.na(Link), paste0(ShortDescription, ' Link: (', Link, ')'), ShortDescription)) %>%
    mutate(Date = ifelse(!is.na(StartYear) & !is.na(EndYear), glue::glue('{StartMonth} {StartYear} --> {EndMonth} {EndYear}',.na = ''), ifelse(!is.na(StartYear), glue::glue('{StartMonth} {StartYear}',.na = ''), '')))
```
# Education

```{r}
data %>%
filter(Topic == "Education") %>%
detailed_entries(what = `ShortDescription`, when = Date, with = SubSubtopic, where = Location, why = LongDescription)
```

# Employment

```{r}
data %>%
filter(Topic == "Employment") %>%
detailed_entries(what = `ShortDescription`, when = Date, with = SubSubtopic, where = Location, why = LongDescription)
```

# Service
## University
```{r}
data %>%
filter(Topic == "Service"& Subtopic == "University") %>%
detailed_entries(what = `ShortDescription`, when = Date, with = SubSubtopic, where = Location, why = LongDescription)
```

## Nonprofit
```{r}
data %>%
filter(Topic == "Service"& Subtopic == "Nonprofit") %>%
detailed_entries(what = `ShortDescription`, when = Date, with = SubSubtopic, where = Location, why = LongDescription)
```

## Government Organizations
```{r}
data %>%
filter(Topic == "Service"& Subtopic == "Government Organizations") %>%
detailed_entries(what = `ShortDescription`, when = Date, with = SubSubtopic, where = Location, why = LongDescription)
```

## Professional Societies
```{r}
data %>%
filter(Topic == "Service"& Subtopic == "Professional Societies") %>%
detailed_entries(what = `ShortDescription`, when = Date, with = SubSubtopic, where = Location, why = LongDescription)
```

## Reviewing for Journals
```{r}
data %>%
filter(Topic == "Service"& Subtopic == "Reviewing for Journals") %>%
detailed_entries(what = `ShortDescription`, when = Date, with = SubSubtopic, where = Location, why = LongDescription)
```

## Society Memberships
```{r}
data %>%
filter(Topic == "Service"& Subtopic == "Society Memberships") %>%
detailed_entries(what = `ShortDescription`, when = Date, with = SubSubtopic, where = Location, why = LongDescription)
```

## Working Groups
```{r}
data %>%
filter(Topic == "Service"& Subtopic == "Working Groups") %>%
detailed_entries(what = `ShortDescription`, when = Date, with = SubSubtopic, where = Location, why = LongDescription)
```

# Publications
## Peer-reviewed Articles
```{r}
data %>%
filter(Topic == "Publications"& Subtopic == "Peer-reviewed Articles") %>%
detailed_entries(what = `ShortDescription`, when = Date, with = SubSubtopic, where = Location, why = LongDescription)
```

## Book Chapters
```{r}
data %>%
filter(Topic == "Publications"& Subtopic == "Book Chapters") %>%
detailed_entries(what = `ShortDescription`, when = Date, with = SubSubtopic, where = Location, why = LongDescription)
```

## Conference Proceedings
```{r}
data %>%
filter(Topic == "Publications"& Subtopic == "Conference Proceedings") %>%
detailed_entries(what = `ShortDescription`, when = Date, with = SubSubtopic, where = Location, why = LongDescription)
```

## Dissertation
```{r}
data %>%
filter(Topic == "Publications"& Subtopic == "Dissertation") %>%
detailed_entries(what = `ShortDescription`, when = Date, with = SubSubtopic, where = Location, why = LongDescription)
```

## Thesis
```{r}
data %>%
filter(Topic == "Publications"& Subtopic == "Thesis") %>%
detailed_entries(what = `ShortDescription`, when = Date, with = SubSubtopic, where = Location, why = LongDescription)
```

## Invited Editorials
```{r}
data %>%
filter(Topic == "Publications"& Subtopic == "Invited Editorials") %>%
detailed_entries(what = `ShortDescription`, when = Date, with = SubSubtopic, where = Location, why = LongDescription)
```

## Acknowledgement on Publications
```{r}
data %>%
filter(Topic == "Publications"& Subtopic == "Acknowledgement on Publications") %>%
detailed_entries(what = `ShortDescription`, when = Date, with = SubSubtopic, where = Location, why = LongDescription)
```

## In the News
```{r}
data %>%
filter(Topic == "Publications"& Subtopic == "In the News") %>%
detailed_entries(what = `ShortDescription`, when = Date, with = SubSubtopic, where = Location, why = LongDescription)
```

## Artistic Contributions
```{r}
data %>%
filter(Topic == "Publications"& Subtopic == "Artistic Contributions") %>%
detailed_entries(what = `ShortDescription`, when = Date, with = SubSubtopic, where = Location, why = LongDescription)
```

# Funding
## Ongoing
```{r}
data %>%
filter(Topic == "Funding"& Subtopic == "Ongoing") %>%
detailed_entries(what = `ShortDescription`, when = Date, with = SubSubtopic, where = Location, why = LongDescription)
```

## Completed
```{r}
data %>%
filter(Topic == "Funding"& Subtopic == "Completed") %>%
detailed_entries(what = `ShortDescription`, when = Date, with = SubSubtopic, where = Location, why = LongDescription)
```

# Teaching
## Course Instructor
```{r}
data %>%
filter(Topic == "Teaching"& Subtopic == "Course Instructor") %>%
detailed_entries(what = `ShortDescription`, when = Date, with = SubSubtopic, where = Location, why = LongDescription)
```

## Workshop Facilitator
```{r}
data %>%
filter(Topic == "Teaching"& Subtopic == "Workshop Facilitator") %>%
detailed_entries(what = `ShortDescription`, when = Date, with = SubSubtopic, where = Location, why = LongDescription)
```

## Professional Development
```{r}
data %>%
filter(Topic == "Teaching"& Subtopic == "Professional Development") %>%
detailed_entries(what = `ShortDescription`, when = Date, with = SubSubtopic, where = Location, why = LongDescription)
```

# Mentoring

```{r}
data %>%
filter(Topic == "Mentoring") %>%
detailed_entries(what = `ShortDescription`, when = Date, with = SubSubtopic, where = Location, why = LongDescription)
```

# Presentations
## Invited
```{r}
data %>%
filter(Topic == "Presentations"& Subtopic == "Invited") %>%
detailed_entries(what = `ShortDescription`, when = Date, with = SubSubtopic, where = Location, why = LongDescription)
```

## Conference Platform
```{r}
data %>%
filter(Topic == "Presentations"& Subtopic == "Conference Platform") %>%
detailed_entries(what = `ShortDescription`, when = Date, with = SubSubtopic, where = Location, why = LongDescription)
```

## Conference Poster
```{r}
data %>%
filter(Topic == "Presentations"& Subtopic == "Conference Poster") %>%
detailed_entries(what = `ShortDescription`, when = Date, with = SubSubtopic, where = Location, why = LongDescription)
```

# Software Competencies
## Languages
```{r}
data %>%
filter(Topic == "Software Competencies"& Subtopic == "Languages") %>%
detailed_entries(what = `ShortDescription`, when = Date, with = SubSubtopic, where = Location, why = LongDescription)
```

## Programs
```{r}
data %>%
filter(Topic == "Software Competencies"& Subtopic == "Programs") %>%
detailed_entries(what = `ShortDescription`, when = Date, with = SubSubtopic, where = Location, why = LongDescription)
```

# Lab Hardwater Competencies

```{r}
data %>%
filter(Topic == "Lab Hardwater Competencies") %>%
detailed_entries(what = `ShortDescription`, when = Date, with = SubSubtopic, where = Location, why = LongDescription)
```

# Field Measurement Competencies

```{r}
data %>%
filter(Topic == "Field Measurement Competencies") %>%
detailed_entries(what = `ShortDescription`, when = Date, with = SubSubtopic, where = Location, why = LongDescription)
```

# Certificates

```{r}
data %>%
filter(Topic == "Certificates") %>%
detailed_entries(what = `ShortDescription`, when = Date, with = SubSubtopic, where = Location, why = LongDescription)
```

# Awards

```{r}
data %>%
filter(Topic == "Awards") %>%
detailed_entries(what = `ShortDescription`, when = Date, with = SubSubtopic, where = Location, why = LongDescription)
```

